Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-06 paper.tex
save

\newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}

@@

@@

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata that can be derived from $p$). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$. In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs $(a, s) \in
{\cal A} \times {\cal S}$, each indicating that signature $s$ is known to
belong to individual $a$.

In this work, author disambiguation is cast into a semi-supervised clustering
problem, as inspired from several previous works described in Section~\ref{related-works}.
Our algorithm is made of four elements: ...

@@

\subsection{Learning a similarity function}
% distance learning as a supervised problem
% balancing difficult and easy cases

@@

>>>>

\newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}
\newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}

@@

\glnote{Note sure if we should talk about matching in this paper?}

@@

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata that can be derived from $p$). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$. In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs $(a, s) \in
{\cal A} \times {\cal S}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$.

In this work, author disambiguation is cast into a semi-supervised clustering
problem, as inspired from several previous works described in Section~\ref
{related-works}. Our algorithm is made of four elements: (i) a blocking
function $b$ whose goal is to rhoughly pre-cluster signatures in order to
reduce computational complexity; (ii) the construction of a similarity function
$d$ between signatures using supervised learning algorithms; (iii) the
semi-supervised clustering of all signatures within a same block, using $d$; (iv) the matching
of predicted clusters to existing profiles in a database.

@@

\subsection{Learning a similarity function}
% distance learning as a supervised problem
% balancing difficult and easy cases
% sampling pairs from block only

@@

\subsection{Blocking}
% compare with torvik & smalheiser (2009) who argue that lnfi blocking has recall around 98%
